---
title: "Homework#5"
author: "Jungyoon Kang"
output: 
  pdf_document: 
    latex_engine: lualatex
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
if (!require(tidyverse)) install.packages('tidyverse')
if (!require(gridExtra)) install.packages('gridExtra')
if (!require(knitr)) install.packages('knitr')
if (!require(kableExtra)) install.packages('kableExtra')
if (!require(rstan)) install.packages('rstan')
if (!require(hBayesDM)) install.packages('hBayesDM')

library(tidyverse)
library(dplyr)
library(gridExtra)
library(knitr)
library(kableExtra)
library(rstan)
library(hBayesDM)
library(cowplot)
library(ggplot2)

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.width = 10, fig.height = 3, fig.align = "center")
```

# Q1
To run this code, run `Q2/Q2_hBayesDM.R` first. 

```{r}
# MLE results from HW2
load('HW2_ra_prospect.RData')

# Hierarchical Bayesian parameter estimation result
load('hBayesDM_output/hBayesDM_ra_prospect.RData')
hbayes_ra_prospect <- output_ra_prospect$all_ind_pars
```

```{r scatterplot function}
draw_scatter_plot <- function(mle_estimates, hbayes_estimates, parameter) {
  x <- mle_estimates[[parameter]]
  y <- hbayes_estimates[[parameter]]
  min_xy = min(x, y)
  max_xy = max(x, y)
  p <- ggplot() +
    geom_point(aes(x = x, y = y)) +
    geom_abline(slope = 1, intercept = 0, colour = 'darkgrey', linetype = 'dashed') +
    xlim(c(min_xy, max_xy)) +
    ylim(c(min_xy, max_xy)) +
    xlab('MLE estimates') +
    ylab('hBayesDM estimates') +
    ggtitle(parameter) +
    theme_bw()
  return(p)
}

```

## (1) hBayesDM vs. MLE
#### hBayesDM (group-level parameters)
```{r}
plot(output_ra_prospect)
```

#### hBayesDM (individual-level parameters)
```{r}
p1 <- plot_ind(output_ra_prospect, "rho")
p2 <- plot_ind(output_ra_prospect, "lambda")
p3 <- plot_ind(output_ra_prospect, "tau")

plot_grid(p1, p2, p3, ncol = 3)
```

#### (2) Visualization 
```{r}
mle_estimates <- df_prospect
hbayes_estimates <- hbayes_ra_prospect

p1 <- draw_scatter_plot(mle_estimates, hbayes_estimates, 'rho')
p2 <- draw_scatter_plot(mle_estimates, hbayes_estimates, 'lambda')
p3 <- draw_scatter_plot(mle_estimates, hbayes_estimates, 'tau')

plot_grid(p1, p2, p3, ncol = 3)
```

## (3) discussion
The hBayesDM uses hierarchical approaches, where individual-level
estimates inform group-level estimates, and group-level estimates constrain individual-level estimates. This leads to “shrinkage” effect, where individual parameter estimates tend to be closer to the group-level estimates, compared to individual-level approahces of the stan results.

\pagebreak

## Q2 
### a) Bayes factor of two models
```{r}
# MLE results from HW2
# The result can be dependent on the seed number

BIC1 = 580.4341
BIC2 = 651.8656

lik_m1 = exp((-1/2) * BIC1)
lik_m2 = exp((-1/2) * BIC2)

BF12 = lik_m1 / lik_m2
```
`r BF12`

### b) evidence of model1 
extreme evidence for model1 (ra_prospect model)

### c) posterior odds
```{r}
prior_m1 = 0.6
prior_m2 = 0.4
post_odds_12 = (prior_m1 / prior_m2) * BF12
```
`r post_odds_12`

### d) posterior model probability of model 1
```{r}
post_m1 = prior_m1 * lik_m1  / (prior_m1 * lik_m1 + prior_m2 * lik_m2)
```
`r post_m1`

### e) Bayes factors of seven memory retention models
```{r}
models <- c("POW1", "POW2", "EXP1", "EXP2", "EXPOW", "HYP1", "HYP2")

bic <- c(475.292, 477.371, 524.532, 489.335, 479.451, 482.954, 481.634) # Get the exact number from HW2
names(bic) <- models

bf_matrix <- matrix(NA, nrow = length(models), ncol = length(models),
                    dimnames = list(Model2 = models, Model1 = models))

for (i in models) {
  for (j in models) {
    delta_bic <- bic[j] - bic[i]  # BIC1 - BIC2
    bf_matrix[i, j] <- formatC(exp(-0.5 * delta_bic), format = "e", digits = 2)
  }
}

kable(bf_matrix, caption = "Bayes Factor (BF₁₂) Table") %>%
  kable_styling(full_width = FALSE, position = "center")
```

# Q3
```{r}
# 
dat = read.table("ra_exampleData.txt", header=T, sep="\t")
allSubjs = unique(dat$subjID)  # all subject IDs
N = length(allSubjs)
# load the output 
load('Q3/output_Q3_ra.RData')
params <- rstan::extract(output_Q3)
```

## (1) Posterior distributions of all 5 subjects
```{r, fig.width= 9, fig.height= 3}
# function for drawing plot
draw.post_dist <- function(output, pars){
  p <- stan_plot(output, show_density = T, pars = pars, ci_level = 0.95, outer_level = 1) +
    labs(title = pars) + 
    theme(plot.title = element_text(face ='bold'))
  return(p)
}

# draw plots!
p1 <- draw.post_dist(output_Q3, 'rho')
p2 <- draw.post_dist(output_Q3, 'lambda')
p3 <- draw.post_dist(output_Q3, 'tau')

# gather plots! 
grid.arrange(p1, p2, p3, ncol = 3)
```

## (2) posterior means of 5 subjects 
```{r}
# Get mean of each subject
mean.rho = apply(params$rho, 2, mean)
mean.lambda = apply(params$lambda, 2, mean)
mean.tau = apply(params$tau, 2, mean)
# create dataframe
Q3.post_mean <- data.frame(subjID <- allSubjs,
                           rho <- mean.rho,
                           lambda <- mean.lambda,
                           tau <- mean.tau)
colnames(Q3.post_mean) <- c('subjID', 'rho', 'lambda', 'tau')

# make table
kable(Q3.post_mean, 'latex', booktabs = TRUE, digits = 3, escape = FALSE,
      caption = 'Posterior means of each subject') %>%
  kable_styling(position = "center", latex_options = 'HOLD_position')
```  

\pagebreak 
