---
title: "HW3"
author: "Jungyoon Kang"
date: "2026-04-21"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
if (!require(tidyverse)) install.packages('tidyverse')
if (!require(gridExtra)) install.packages('gridExtra')
if (!require(knitr)) install.packages('knitr')
if (!require(kableExtra)) install.packages('kableExtra')
if (!require(rstan)) install.packages('rstan')

library(tidyverse)
library(gridExtra)
library(knitr)
library(kableExtra)
library(rstan)
library(cowplot)

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.width = 10, fig.height = 3, fig.align = "center")
```


# 1.

```{r cars}
# set the year probabilities
freshman <- 0.15
sophomore <- 0.20
junior <- 0.25
senior <- 0.40

# make table of the contiditonal probabilites (p(tv|year))

rm <- c(0.15, 0.1, 0.1, 0.6)
la <- c(0.25, 0.3, 0.2, 0.1)
hy <- c(0.3, 0.2, 0.3, 0.2)
ia <- c(0.3, 0.4, 0.4, 0.1)

data <- data.frame(rm, la, hy, ia)
rows <- c('Freshman', 'Sophomore', 'Junior', 'Senior')
row.names(data) <- rows
```


```{r}
# Calculate joint probabilities
fre_tvs <- freshman * data[1,]; sop_tvs <- sophomore * data[2,]
jun_tvs <- junior * data[3,]; sen_tvs <- senior * data[4,]
joint <-  data.frame(rbind(fre_tvs, sop_tvs, jun_tvs, sen_tvs))
cols <- c('RunningMan', 'Ilivealone', 'HangingoutwithYoo', 'IamSolo')
colnames(joint) <- cols
```

```{r}
#calculate marginal probabilities
total_year <- c(sum(joint[1,]), sum(joint[2,]), sum(joint[3,]), sum(joint[4,]))
total <- cbind(joint, total_year)
total_tv <- c(sum(total$RunningMan), sum(total$Ilivealone), 
                sum(total$HangingoutwithYoo), sum(total$IamSolo), 
                sum(total$total_year))
total <- rbind(total, total_tv)
row.names(total) <- c(rows, 'total_tv')
total
```
### Joint probability
### The table above contains joint probabilities and marginal probabilities. The joint probabilities were calculated by multiplying the probability of a college year (p(college year)) with the probability of a TV show given college year (p(TV show|college year)). For example, p(Freshman, Running Man) = p(Freshman) x p(Running Man|Freshman) = 0.15 x 0.4 = 0.06.

```{r}
# Check independence
independence <- data.frame()
for (i in c(1:4)) {
  ind <- total[5,1:4] * total$total_year[i]
  independence<- rbind(independence, ind)
  }
colnames(independence) <- cols; row.names(independence) <- rows
independence
```
### Check independence
### I also tested whether college year and TV show are independent or not. If A and B are independent, p(A, B) = p(A) x p(B). Therefore, to test for independence, I caculated p(college year) x p(TV show) and compared the result with p(college year, TV show). The table below shows if p(college year, TV show) is equal to p(college year) x p(TV show). If they are equal, the entry will be marked as "TRUE", and if they are not equal, the entry will be marked as "FALSE".

```{r}
independence == joint
```
### As you can see from the table, none of the joint probabilities match the product of their respective marginal probabilities. For instance, p(freshman) x p(Running man) is 0.046125, whereas p(freshman, Running man) is 0.0225. This implies that college year and TV show are not independent.

\newpage

# 2

### To answer each of the questions, we need to calculate the conditional probability of having COVID given that a person tested positive, which is denoted as p(COVID|positive). 

### p(COVID|positive) = p(COVID, positive) / p(positive) 
###                   = p(positive|COVID) x p(COVID) / p(COVID) x p(positive|COVID) + p(no COVID) x p(positive|no COVID)



## 2-(1)

```{r}
# o = having COVID; x = not having COVID
# + = positive; - = negative

hit_rate <- 0.9    # hit_rate = p(+|o) = p(+, o)/p(o)
FA <- 0.04    # false_alarm(FA) = p(+|x) = p(+, x)/p(x)
o <- 20000/50000000   # p(o) (having COVID)
x <- 1-o # p(negative) = 1- p(positive)
pos_o <- o * hit_rate # pos_o = p(+, o) = p(o)*p(+|o)
pos_x <- x * FA # pos_x = p(+, x) = p(x)*p(+|x)

# calculate p(COVID|positive) = p(o|+)
# p(o,+)/p(o) = p(+|o)*p(o)/(p(o)*p(+|o)+p(x)*p(+|x))
covid_given_pos <- pos_o / (pos_o+pos_x)
cat("answer = ", covid_given_pos)

```

## 2-(2)
```{r}

# false_negative (FN) = p(negative|COVID) = p(-|o) 
FN2 = 0.1 # false_negative (FN) = p(-|o) = p(-, o)/p(o)
hit_rate2 = 1- FN2 # p(-|o) + p(+|o) = 1
FA2 = 0.04 # false_alarm(FA) = p(+|x) = p(+, x)/p(x)
o2 <- 20000/50000000   # p(o) (having COVID)
x2 <- 1-o2 # p(x) (p(negative) = 1- p(positive))
pos_o2 <- o2 * hit_rate2 # pos_o = p(+, o) = p(o)*p(+|o)
pos_x2 <- x2 * FA2 # pos_x = p(+, x) = p(x)*p(+|x)

# calculate p(COVID|positive) = p(o|+) 
# p(o,+)/p(o) = p(+|o)*p(o)/(p(o)*p(+|o)+p(x)*p(+|x))
covid_given_pos2 <- pos_o2 / (pos_o2+pos_x2)
cat("answer = ", covid_given_pos2)
```

## 2-(3)
```{r}
# false_negative (FN) = p(negative|COVID) = p(-|o) 
FN3 = 0.1 # false_negative (FN) = p(-|o) = p(-, o)/p(o)
hit_rate3 = 1- FN2 # p(-|o) + p(+|o) = 1
FA3 = 0.04 # false_alarm(FA) = p(+|x) = p(+, x)/p(x)
o3 <- 0.05   # p(o) (having COVID)
x3 <- 1-o3 # p(x) (p(negative) = 1- p(positive))
pos_o3 <- o3 * hit_rate3 # pos_o = p(+, o) = p(o)*p(+|o)
pos_x3 <- x3 * FA3 # pos_x = p(+, x) = p(x)*p(+|x)

# calculate p(COVID|positive) = p(o|+) 
# p(o,+)/p(o) = p(+|o)*p(o)/(p(o)*p(+|o)+p(x)*p(+|x))
covid_given_pos3 <- pos_o3 / (pos_o3+pos_x3)
cat("answer = ", covid_given_pos3)
```